---
title: Time Varying Distribution Parameter in the Stratified Proportional Fishery
  Indices?
date: "Last updated on October 8, 2018"
output:
  html_document:
    df_print: paged
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(knitr)
library(lattice)
```

```{r include=FALSE}
load("Data/2018era spfi distribution parameter analysis.RData")
```

```{r eval=TRUE, include=FALSE}
#quick helper function to summarize results
distrib_param_tables <- function(x) {
#inits
 nsim    = dim(x)[1]
 nstocks = dim(x)[2]
 nages   = dim(x)[3]
 stknames = colnames(x)
 tmp1 = list()
#loop
 for (i in 1:nstocks) {
  tmp2 = x[,i,1:nages]
  tmp2[,colSums(tmp2)==0] = NA
  tmp2 = cbind(c(stknames[i],rep("",nsim-1)),round(tmp2,2))
  colnames(tmp2)[1] = "Stock"
  tmp1[[i]] = tmp2
 }
#return out
 return(tmp1)
}
```

# Introduction: 2018ERA SPFIs
## HRJ Database

2018ERA HRJ files found on SharePoint. Read into R via the following code:

```{r include=TRUE, eval=FALSE}
 #Read in HRJ files in a directory
  by=readHRJdir("<user directory>", nFisheries=79, straysinescap=TRUE, Age6="include")
 #Convert to CY layout
  cy=convertHRJ_BYtoCY(by)
 #Convert HRJ from R to Access format
  z.cy=convertHRJ_RtoAccess(cy)
 #add the 'preferred' table to the Access format
  z.cy = addPTableHRJ(z.cy, hrjclass = "Access")
```

## SEAK
### Stock & Ages

```{r eval=TRUE}
  kable(seak$stockage)
```

### AEQ Total Mortality

```{r eval=TRUE}
  kable(round(summary(x=seak_spfi, unit="aeq tot")$spfi,2))
```

### AEQ Landed Catch

```{r eval=TRUE}
  kable(round(summary(x=seak_spfi, unit="aeq cat")$spfi,2))
```

## NBC
### Stock & Ages

```{r eval=TRUE}
  kable(nbc$stockage)
```

### AEQ Total Mortality

```{r eval=TRUE}
  kable(round(summary(x=nbc_spfi, unit="aeq tot")$spfi,2))
```

### AEQ Landed Catch

```{r eval=TRUE}
  kable(round(summary(x=nbc_spfi, unit="aeq cat")$spfi,2))
```

## WCVI
### Stock & Ages

```{r eval=TRUE}
  kable(wcvi$stockage)
```

### AEQ Total Mortality

```{r eval=TRUE}
  kable(round(summary(x=wcvi_spfi, unit="aeq tot")$spfi,2))
```

### AEQ Landed Catch

```{r eval=TRUE}
  kable(round(summary(x=wcvi_spfi, unit="aeq cat")$spfi,2))
```

# Methods
## Analysis 1

```{r eval=FALSE}
 #compute spfi for different year blocks
  #seak
   seak_spfi_a1 = multispfi(spfi_input = seak, yearvec = 1994:2016, hrjdat = z.cy, hrjtype = "P")
   seak_spfi_a1_results_dist  = multispfidistfun(spfi_output_list=seak_spfi_a1, spfi_input=seak)
   seak_spfi_a1_results_cwthr = multispficwthrfun(spfi_output_list=seak_spfi_a1, spfi_input=seak)
  #nbc
   nbc_spfi_a1 = multispfi(spfi_input = nbc, yearvec = 1994:2016, hrjdat = z.cy, hrjtype = "P")
   nbc_spfi_a1_results_dist  = multispfidistfun(spfi_output_list=nbc_spfi_a1, spfi_input=nbc)
   nbc_spfi_a1_results_cwthr = multispficwthrfun(spfi_output_list=nbc_spfi_a1, spfi_input=nbc)
  #wcvi
   wcvi_spfi_a1 = multispfi(spfi_input = wcvi, yearvec = 1999:2016, hrjdat = z.cy, hrjtype = "P")
   wcvi_spfi_a1_results_dist  = multispfidistfun(spfi_output_list=wcvi_spfi_a1, spfi_input=wcvi)
   wcvi_spfi_a1_results_cwthr = multispficwthrfun(spfi_output_list=wcvi_spfi_a1, spfi_input=wcvi)
```

## Analysis 2

```{r eval=FALSE}
 #compute spfi for different year blocks
  #seak
   seak_spfi_a2 = multispfi(spfi_input = seak, yearvec = list(1979:1998, 1999:2008, 2009:2016), hrjdat = z.cy, hrjtype = "P")
   seak_spfi_a2_results_dist = multispfidistfun(spfi_output_list=seak_spfi_a2, spfi_input=seak)
  #nbc
   nbc_spfi_a2 = multispfi(spfi_input = nbc , yearvec = list(1979:1998, 1999:2008, 2009:2016), hrjdat = z.cy, hrjtype = "P")
   nbc_spfi_a2_results_dist = multispfidistfun(spfi_output_list=nbc_spfi_a2 , spfi_input=nbc)
  #wcvi
   wcvi_spfi_a2 = multispfi(spfi_input = wcvi, yearvec = list(1979:1998, 1999:2008, 2009:2016), hrjdat = z.cy, hrjtype = "P")
   wcvi_spfi_a2_results_dist = multispfidistfun(spfi_output_list=wcvi_spfi_a2, spfi_input=wcvi)
```

# Results
## Analysis 1
### SEAK
#### Winter/Spring

```{r eval=TRUE, fig.height=5, fig.width=6.5}
   xyplot(distrib~ERAYear|Age,group=~Stock,type="l",data=subset(seak_spfi_a1_results_dist,strata==1),auto.key=list(columns=2,title="Stock",space="right"),main="Winter/Spring")
```

```{r eval=TRUE}
x=with(subset(seak_spfi_a1_results_dist,strata==1), tapply(distrib, list(ERAYear,Stock,Age), mean))
kable(do.call("rbind",distrib_param_tables(x)))
```

#### June Outside

```{r eval=TRUE, fig.height=5, fig.width=6.5}
   xyplot(distrib~ERAYear|Age,group=~Stock,type="l",data=subset(seak_spfi_a1_results_dist,strata==2),auto.key=list(columns=2,title="Stock",space="right"),main="June Outside")
```

```{r eval=TRUE}
x=with(subset(seak_spfi_a1_results_dist,strata==2), tapply(distrib, list(ERAYear,Stock,Age), mean))
kable(do.call("rbind",distrib_param_tables(x)))
```

#### June Inside

```{r eval=TRUE, fig.height=5, fig.width=6.5}
   xyplot(distrib~ERAYear|Age,group=~Stock,type="l",data=subset(seak_spfi_a1_results_dist,strata==3),auto.key=list(columns=2,title="Stock",space="right"),main="June Inside")
```

```{r eval=TRUE}
x=with(subset(seak_spfi_a1_results_dist,strata==3), tapply(distrib, list(ERAYear,Stock,Age), mean))
kable(do.call("rbind",distrib_param_tables(x)))
```

#### July Outside/Fall

```{r eval=TRUE, fig.height=5, fig.width=6.5}
   xyplot(distrib~ERAYear|Age,group=~Stock,type="l",data=subset(seak_spfi_a1_results_dist,strata==4),auto.key=list(columns=2,title="Stock",space="right"),main="July Outside/Fall")
```

```{r eval=TRUE}
x=with(subset(seak_spfi_a1_results_dist,strata==4), tapply(distrib, list(ERAYear,Stock,Age), mean))
kable(do.call("rbind",distrib_param_tables(x)))
```

#### July Inside

```{r eval=TRUE, fig.height=5, fig.width=6.5}
   xyplot(distrib~ERAYear|Age,group=~Stock,type="l",data=subset(seak_spfi_a1_results_dist,strata==5),auto.key=list(columns=2,title="Stock",space="right"),main="July Inside")
```

```{r eval=TRUE}
x=with(subset(seak_spfi_a1_results_dist,strata==5), tapply(distrib, list(ERAYear,Stock,Age), mean))
kable(do.call("rbind",distrib_param_tables(x)))
```

### NBC
#### All strata

```{r eval=TRUE, fig.height=5, fig.width=6.5}
   xyplot(distrib~ERAYear|Age,group=~Stock,type="l",data=subset(nbc_spfi_a1_results_dist,strata==1),auto.key=list(columns=2,title="Stock",space="right"))
```

```{r eval=TRUE}
x=with(subset(nbc_spfi_a1_results_dist,strata==1), tapply(distrib, list(ERAYear,Stock,Age), mean))
kable(do.call("rbind",distrib_param_tables(x)))
```

### WCVI
#### Fall/Winter

```{r eval=TRUE, fig.height=5, fig.width=6.5}
   xyplot(distrib~ERAYear|Age,group=~Stock,type="l",data=subset(wcvi_spfi_a1_results_dist,strata==1),auto.key=list(columns=2,title="Stock",space="right"),main="Fall/Winter")
```

```{r eval=TRUE}
x=with(subset(wcvi_spfi_a1_results_dist,strata==1), tapply(distrib, list(ERAYear,Stock,Age), mean))
kable(do.call("rbind",distrib_param_tables(x)))
```

#### Spring

```{r eval=TRUE, fig.height=5, fig.width=6.5}
   xyplot(distrib~ERAYear|Age,group=~Stock,type="l",data=subset(wcvi_spfi_a1_results_dist,strata==2),auto.key=list(columns=2,title="Stock",space="right"),main="Spring")
```

```{r eval=TRUE}
x=with(subset(wcvi_spfi_a1_results_dist,strata==2), tapply(distrib, list(ERAYear,Stock,Age), mean))
kable(do.call("rbind",distrib_param_tables(x)))
```

#### Summer

```{r eval=TRUE, fig.height=5, fig.width=6.5}
   xyplot(distrib~ERAYear|Age,group=~Stock,type="l",data=subset(wcvi_spfi_a1_results_dist,strata==3),auto.key=list(columns=2,title="Stock",space="right"),main="Summer")
```

```{r eval=TRUE}
x=with(subset(wcvi_spfi_a1_results_dist,strata==3), tapply(distrib, list(ERAYear,Stock,Age), mean))
kable(do.call("rbind",distrib_param_tables(x)))
```

## Analysis 2
### SEAK
#### Winter/Spring

```{r eval=TRUE, fig.height=5, fig.width=6.5}
   xyplot(distrib~factor(Simulation)|Age,group=~Stock,type="l",data=subset(seak_spfi_a2_results_dist,strata==1),auto.key=list(columns=2,title="Stock",space="right"),main="Winter/Spring")
```

```{r eval=TRUE}
x=with(subset(seak_spfi_a2_results_dist,strata==1), tapply(distrib, list(Simulation,Stock,Age), mean))
kable(do.call("rbind",distrib_param_tables(x)))
```

#### June Outside

```{r eval=TRUE, fig.height=5, fig.width=6.5}
   xyplot(distrib~factor(Simulation)|Age,group=~Stock,type="l",data=subset(seak_spfi_a2_results_dist,strata==2),auto.key=list(columns=2,title="Stock",space="right"),main="June Outside")
```

```{r eval=TRUE}
x=with(subset(seak_spfi_a2_results_dist,strata==2), tapply(distrib, list(Simulation,Stock,Age), mean))
kable(do.call("rbind",distrib_param_tables(x)))
```

#### June Inside

```{r eval=TRUE, fig.height=5, fig.width=6.5}
   xyplot(distrib~factor(Simulation)|Age,group=~Stock,type="l",data=subset(seak_spfi_a2_results_dist,strata==3),auto.key=list(columns=2,title="Stock",space="right"),main="June Inside")
```

```{r eval=TRUE}
x=with(subset(seak_spfi_a2_results_dist,strata==3), tapply(distrib, list(Simulation,Stock,Age), mean))
kable(do.call("rbind",distrib_param_tables(x)))
```

#### July Outside/Fall

```{r eval=TRUE, fig.height=5, fig.width=6.5}
   xyplot(distrib~factor(Simulation)|Age,group=~Stock,type="l",data=subset(seak_spfi_a2_results_dist,strata==4),auto.key=list(columns=2,title="Stock",space="right"),main="July Outside/Fall")
```

```{r eval=TRUE}
x=with(subset(seak_spfi_a2_results_dist,strata==4), tapply(distrib, list(Simulation,Stock,Age), mean))
kable(do.call("rbind",distrib_param_tables(x)))
```

#### July Inside

```{r eval=TRUE, fig.height=5, fig.width=6.5}
   xyplot(distrib~factor(Simulation)|Age,group=~Stock,type="l",data=subset(seak_spfi_a2_results_dist,strata==5),auto.key=list(columns=2,title="Stock",space="right"),main="July Inside")
```

```{r eval=TRUE}
x=with(subset(seak_spfi_a2_results_dist,strata==5), tapply(distrib, list(Simulation,Stock,Age), mean))
kable(do.call("rbind",distrib_param_tables(x)))
```

### NBC
#### All strata

```{r eval=TRUE, fig.height=5, fig.width=6.5}
   xyplot(distrib~factor(Simulation)|Age,group=~Stock,type="l",data=subset(nbc_spfi_a2_results_dist,strata==1),auto.key=list(columns=2,title="Stock",space="right"))
```

```{r eval=TRUE}
x=with(subset(nbc_spfi_a2_results_dist,strata==1), tapply(distrib, list(Simulation,Stock,Age), mean))
kable(do.call("rbind",distrib_param_tables(x)))
```

### WCVI
#### Fall/Winter

```{r eval=TRUE, fig.height=5, fig.width=6.5}
   xyplot(distrib~factor(Simulation)|Age,group=~Stock,type="l",data=subset(wcvi_spfi_a2_results_dist,strata==1),auto.key=list(columns=2,title="Stock",space="right"),main="Fall/Winter")
```

```{r eval=TRUE}
x=with(subset(wcvi_spfi_a2_results_dist,strata==1), tapply(distrib, list(Simulation,Stock,Age), mean))
kable(do.call("rbind",distrib_param_tables(x)))
```

#### Spring

```{r eval=TRUE, fig.height=5, fig.width=6.5}
   xyplot(distrib~factor(Simulation)|Age,group=~Stock,type="l",data=subset(wcvi_spfi_a2_results_dist,strata==2),auto.key=list(columns=2,title="Stock",space="right"),main="Spring")
```

```{r eval=TRUE}
x=with(subset(wcvi_spfi_a2_results_dist,strata==2), tapply(distrib, list(Simulation,Stock,Age), mean))
kable(do.call("rbind",distrib_param_tables(x)))
```

#### Summer

```{r eval=TRUE, fig.height=5, fig.width=6.5}
   xyplot(distrib~factor(Simulation)|Age,group=~Stock,type="l",data=subset(wcvi_spfi_a2_results_dist,strata==3),auto.key=list(columns=2,title="Stock",space="right"),main="Summer")
```

```{r eval=TRUE}
x=with(subset(wcvi_spfi_a2_results_dist,strata==3), tapply(distrib, list(Simulation,Stock,Age), mean))
kable(do.call("rbind",distrib_param_tables(x)))
```
